\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2022-11-09 doc/USER_MANUAL/02_getting_started.tex

To download the SPECFEM3D\_Cartesian software package, type this:
\begin{verbatim}
git clone --recursive --branch devel https://github.com/geodynamics/specfem3d.git
\end{verbatim}
%

@@

You can add \texttt{-{}-enable-vectorization} to the configuration options to speed up the code in the fluid (acoustic) and elastic parts.
This works fine if (and only if) your computer always allocates a contiguous memory block for each allocatable array;
this is the case for most machines and most compilers, but not all. To disable this feature, use option \texttt{-{}-disable-vectorization}.
For more details see \href{https://github.com/geodynamics/specfem3d/issues/81}{github.com/geodynamics/specfem3d/issues/81} .
To check if that option works fine on your machine, run the code with and without it for an acoustic/elastic model and make sure the seismograms are identical.\\

@@

If you want to develop new features in the code, and/or if you want to make small changes, improvements, or bug fixes, you are very welcome to contribute. To do so, i.e. to access the development branch of the source code with read/write access (in a safe way, no need to worry too much about breaking the package, there are CI tests based on BuildBot, Travis-CI and Jenkins in place that are checking and validating all new contributions and changes), please visit this Web page:\\
\url{https://github.com/geodynamics/specfem3d/wiki}

>>>>

To download the SPECFEM3D\_Cartesian software package, type this:
\begin{verbatim}
git clone --recursive --branch devel https://github.com/SPECFEM/specfem3d.git
\end{verbatim}
%

@@

You can add \texttt{-{}-enable-vectorization} to the configuration options to speed up the code in the fluid (acoustic) and elastic parts.
This works fine if (and only if) your computer always allocates a contiguous memory block for each allocatable array;
this is the case for most machines and most compilers, but not all. To disable this feature, use option \texttt{-{}-disable-vectorization}.
For more details see \href{https://github.com/SPECFEM/specfem3d/issues/81}{github.com/SPECFEM/specfem3d/issues/81} .
To check if that option works fine on your machine, run the code with and without it for an acoustic/elastic model and make sure the seismograms are identical.\\

@@

If you want to develop new features in the code, and/or if you want to make small changes, improvements, or bug fixes, you are very welcome to contribute. To do so, i.e. to access the development branch of the source code with read/write access (in a safe way, no need to worry too much about breaking the package, there are CI tests based on BuildBot, Travis-CI and Jenkins in place that are checking and validating all new contributions and changes), please visit this Web page:\\
\url{https://github.com/SPECFEM/specfem3d/wiki}

### 2022-11-09 doc/USER_MANUAL/15_informations_for_developers.tex

You can get a very simple 1D version of a demo code (there is one in Fortran and one in Python):
\begin{verbatim}
git clone --recursive https://github.com/geodynamics/specfem1d.git
\end{verbatim}

@@

\noindent For information on how to contribute to the code, i.e., for how to make your modifications, additions or improvements part of the
official package, see \url{https://github.com/geodynamics/specfem3d/wiki} .

>>>>

You can get a very simple 1D version of a demo code (there is one in Fortran and one in Python):
\begin{verbatim}
git clone --recursive https://github.com/SPECFEM/specfem1d.git
\end{verbatim}

@@

\noindent For information on how to contribute to the code, i.e., for how to make your modifications, additions or improvements part of the
official package, see \url{https://github.com/SPECFEM/specfem3d/wiki} .
